State of the Practice for Medical Imaging Software Based on Open Source Repositories

### 2024-11-26 StateOfPractice/Papers/SOP_MI_CritReviewsBioMedEng/AddressConcerns_LetterToEditor.tex
Letter to editor revised submission

\begin{letter}{~\\
~\\
~\\
~\\
Dr.\ Anthony McGoron\\
Editor-in-Chief\\
Critical Reviews in Biomedical Engineering\\
~\\
{\bf Re: Review Article Submission}}

@@

We are submitting for your consideration a review article titled ``State of the
Practice for Medical Imaging Software Based on Open Source Repositories''.  This
article has not been published elsewhere and it has not been simultaneously
submitted for publication elsewhere. We have published a significantly extended
paper on the same topic on the arXiv.

We review the state of the practice for the development of Medical Imaging (MI)
software based on data available in open source repositories. We identify the
open source packages available, rank them by their application of software
engineering best practices, compare MI software to other research software and
provide recommendations to potentially improve MI software quality going
forward.

We suggest the following reviewers:

\begin{itemize}
    \item \href{https://bme.ubc.ca/?directory=alexander-weber} {Dr.\ Alexander Weber}: \texttt{aweber@bcchr.ca}
    \item \href{https://www.robarts.ca/scholl_group/people/bio/akbari_alireza.html} {Dr.\ Alireza Akbari}: \texttt{aakbari@uwo.ca}
    \item \href{https://www.se.informatik.uni-kiel.de/en/team/prof.-dr.-wilhelm-willi-hasselbring} {Dr.\ Wilhelm Hasselbring}: \texttt{hasselbring@email.uni-kiel.de}
\end{itemize}

Thank you for considering our work for publication in your journal.  If you have
any questions or concerns, please let me know.

>>>>

\begin{letter}{~\\
~\\
~\\
~\\
Dr.\ Anthony McGoron\\
Editor-in-Chief\\
Critical Reviews in Biomedical Engineering\\
~\\
{\bf Re: Revisions to Review Article}}

@@

Thank you for expressing your concerns. To address them, we are submitting a
revised version of our paper ``State of the Practice for Medical Imaging
Software Based on Open Source Repositories''.  The text has been modified to
eliminate the textual similarity to our paper: Smith, S., Michalski, P.,
Carette, J. et al.\ State of the Practice for Lattice Boltzmann Method Software.
Archives of Computational Methods in Engineering 31, 313--350 (2024).

The ``State of the Practice for Lattice Boltzmann Method Software'' paper is
frequently cited in the non-redacted version of our submission. Those citations
were redacted for the purpose of the double blind review.

Thank you for considering our work for publication in your journal.  If you have
any further questions or concerns, please let me know.
